---
title: "TidyTemplate"
date: 2022-01-04
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

#knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(jsonlite)
library(janitor)
library(fastmap)
library(gt)
library(emojifont)
library(paletteer)
library(webshot)
```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

#tt <- tt_load("2021-08-17")
# this week is bring your own data week

# load data from census api
url <- 'https://api.census.gov/data/2019/acs/acs5?get=group(B15003)&for=state:*'
dat <- fromJSON(url) %>%  
  as.data.frame() %>% 
  row_to_names(row_number = 1) %>% 
  select(NAME , state , ends_with("E"))

# load variable names from census
var_url <- 'https://api.census.gov/data/2019/acs/acs5/variables'
var_names <- fromJSON(var_url) %>%  
  as.data.frame() %>% 
  row_to_names(row_number = 1)

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

#tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

#tt %>% map(glimpse)
str(dat)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
dat2 <- dat %>% 
  #filter( ! (NAME %in% c('District of Columbia' , 'Puerto Rico') )) %>% 
  pivot_longer(cols = B15003_001E:B15003_025E ,
               names_to = 'var_name' ,
               values_to = 'qty' ) %>% 
  left_join(var_names , by= c('var_name' = 'name')) %>% 
  mutate(qty = as.integer(qty)) %>% 
  select(NAME , state , qty , label ) %>% 
  mutate(label = ifelse(label == 'Estimate!!Total:' , 'Population' , label)) %>% 
  mutate(label = str_replace_all(label , 'Estimate!!Total:!!' , '' )) %>% 
  pivot_wider(names_from = label , values_from = qty) 
  

dat2$less_than_hs <- rowSums(dat2[4:18])
dat2$hs <- rowSums(dat2[19:20])
dat2$some_college <- rowSums(dat2[21:23])
dat2$bachelor_degree <- rowSums(dat2[24])
dat2$grad_degree <- rowSums(dat2[25:26])
dat2$doctorate_degree <- rowSums(dat2[27])
dat2$four_year_degree <- rowSums(dat2[24:27])


#dat2$check_total <- rowSums(dat2[28:33])
#dat2$check <- dat2$`Population` == dat2$check_total


dat2 <- dat2 %>% select(c(1:3 , 28:34))


dat3 <- dat2 %>% 
  mutate(`No High School` = (less_than_hs / `Population`)*100 , 
         `High School` = (hs/`Population`)*100 ,
         `Some College` = (some_college/`Population`)*100 ,
         `Bachelor` = (bachelor_degree/`Population`)*100 ,
         `Graduate` = (grad_degree/`Population`)*100 ,
         `Doctorate` = (doctorate_degree/`Population`)*100 , 
         `Four Year Degree` = (four_year_degree/`Population`)*100) %>% 
  select(NAME ,3, 11:17)


# function that will return html formatted bar chart
bar_chart <- function(value, color = "red", display_value = NULL){
  
  # Choose to display percent of total
  if (is.null(display_value)) {
    display_value <- "&nbsp;"
  } else {
    display_value <- display_value
  }
  
  # paste color and value into the html string
  glue::glue("<span style=\"display: inline-block; direction: ltr; border-radius: 4px; padding-right: 2px; background-color: {color}; color: {color}; width: {value}%\">&nbsp;</span><span style=\" font-weight: bold;  display: fixed;\">&nbsp;&nbsp;{display_value}</span>")
}


dat3 <- dat3 %>% 
  mutate(
    four_year = `Four Year Degree`,
    bar_chart = bar_chart(`Four Year Degree`, 
                          color = "dodgerblue" , 
                          display_value = round(`Four Year Degree`,1)),
    bar_chart = map(bar_chart, ~gt::html(as.character(.x))) , 
    `Four Year Degree` = bar_chart ) %>% 
  select(-bar_chart)

```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
p <- dat3 %>% 
  arrange(desc(four_year)) %>% 
  select(-four_year) %>% 
  mutate(id = row_number() ) %>% 
  select(id,1:9) %>% 
  gt() %>%
  tab_header(
    title = md("**Educational Attainment per State**"),
    subtitle = "In Descending Order by 4-Year Degree"
  ) %>% 
  tab_source_note(
    source_note = md("Data: US Census American Community Survey (ACS) 5-Year 2019<br>Table: Nat Rivera @itsnatrivera")
  ) %>% 
  tab_footnote(
    footnote = md("**% of Total**"),
    locations = cells_column_labels(4:9)
  ) %>% 
  tab_footnote(
    footnote = md("**Population of people 25 years old or greater.**"),
    locations = cells_column_labels(3)
  ) %>% 
  tab_spanner(
    label = md("**State & Population**"),
    columns = c(NAME, `Population`)
  ) %>%
  tab_spanner(
    label = md("**Educational Attainment Level %**"),
    columns = c(`No High School`:`Doctorate`)
  ) %>% 
  tab_spanner(
    label = md("**At Least 4 Year Degree %**"),
    columns = c(`Four Year Degree`)
  ) %>% 
  cols_align(
    align = "left" ,
    columns = c(`Four Year Degree`)
  ) %>% 
  cols_label(
    `Four Year Degree` = "Bachelor or Higher",
    id = ""
  ) %>% 
  fmt_number(
    columns = c(`No High School`:`Doctorate`),
    decimals = 1
  ) %>% 
  fmt_number(
    columns = `Population` ,
    decimals = 0 ,
    use_seps = TRUE
  ) %>% 
  cols_align(
    align = "right" ,
    columns = `No High School`:`Doctorate`
  ) %>% 
  data_color(
    columns = 3, 
    colors = scales::col_numeric(
      palette = paletteer::paletteer_d(
        palette = "ggsci::blue_material"
      ) %>% as.character(),
      domain = NULL
    )
  ) %>% 
  tab_options(
    table.margin.left =  pct(2),
    table.margin.right =  pct(2),
  )
p
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave( 
  filename = "My TidyTuesday Plot.png",
  device = "png")

```



```{r}
# export the gt table
gtsave(data = p, filename = "My TidyTuesday Plot.png", path = NULL)
```

