---
title: "TidyTemplate"
date: 2021-09-12
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-09-07") # load data

# load country-nationality data
# url https://github.com/knowitall/chunkedextractor/blob/master/src/main/resources/edu/knowitall/chunkedextractor/demonyms.csv
nat_url <- 'https://raw.githubusercontent.com/knowitall/chunkedextractor/master/src/main/resources/edu/knowitall/chunkedextractor/demonyms.csv'
nats <- read.csv(nat_url)
colnames(nats) <- c('nat' , 'country')

```




# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}


# copy tables to memory
races <- tt$races
circuits <- tt$circuits
results <- tt$results
drivers <- tt$drivers
constructors <- tt$constructors

# prepare data in driver table for join
drivers$driver_nationality <- drivers$nationality
drivers$driver_nun <- drivers$number
drivers$driverId <- as.integer(drivers$driverId )
drivers$driver_nationality <- ifelse(
  drivers$driver_nationality == 'East German' ,
  'German' ,
  drivers$driver_nationality
)
drivers$driver_nationality <- ifelse(
  drivers$driver_nationality == 'Monegasque' ,
  'Monégasque' ,
  drivers$driver_nationality
)
drivers$driver_nationality <- ifelse(
  drivers$driver_nationality == 'American-Italian' ,
  'Italian' ,
  drivers$driver_nationality
)
drivers$driver_nationality <- ifelse(
  drivers$driver_nationality == 'Argentine-Italian' ,
  'Italian' ,
  drivers$driver_nationality
)
drivers <- drivers %>% select(-nationality , -url , -number)

# prepare data in constructors table for join
constructors$con_nationality <- constructors$nationality
constructors$con_name <- constructors$name
constructors$con_nationality <- ifelse(
  constructors$con_nationality == 'Belgium' , 
  'Belgian' , 
  constructors$con_nationality )
constructors$con_nationality <- ifelse(
  constructors$con_nationality == 'East German' , 
  'German' , 
  constructors$con_nationality )
constructors <- constructors %>% select(-nationality , -url , -name)

# prepare data in races table for join
races$race_date <- races$date
races$race_time <- races$time
races <- races %>% select(-url , -date , -time)

# prepare data in circuits table for join
circuits$circuit_name <- circuits$name
circuits$country <- ifelse(circuits$country == 'UK' , 
                           'United Kingdom' , 
                           circuits$country)
circuits <- circuits %>% select(-name , -alt , -url)


```



```{r}
drivers <- drivers %>% 
  left_join(y=nats , by=c('driver_nationality' = 'nat')) %>% 
  mutate(driver_country = country) %>% 
  select(-country)

constructors <- constructors %>% 
  left_join(y=nats , by=c('con_nationality' = 'nat')) %>% 
  mutate(con_country = country) %>% 
  select(-country)
```




```{r}
# join data
race_data <- results %>% 
  left_join(y=drivers , by = 'driverId') %>% 
  left_join(y=constructors , by='constructorId') %>% 
  left_join(y=races , by='raceId') %>% 
  left_join(y=circuits , by='circuitId')

# add a boolean for driver country = race country
race_data$driver_home <- ifelse(
  race_data$country == race_data$driver_country ,
  1,0)

# add a boolean for constructor country = race country
race_data$con_home <- ifelse(
  race_data$country == race_data$con_country ,
  1,0)

# create a sub df with the drivers in position = 1
race_data_win <- race_data %>% filter(position == 1)
```



```{r}
# percentage of constructors at home
mean(race_data$con_home)*100
```

```{r}
# percentage of drivers at home
mean(race_data$driver_home)*100
```

```{r}
# percentage of constructor at home who won
mean(race_data_win$con_home)*100
```

```{r}
# percentage of drivers at home who won
mean(race_data_win$driver_home)*100
```


```{r}
# plot constructor all racers vs winners at home
barplot(
  c(ALL=mean(race_data$con_home) *100 , 
    WIN=mean(race_data_win$con_home)*100) ,
  main = 'Constructor At Home by %'
  ) 
```


```{r}
# plot driver all racers vs winners at home
barplot(
  c(ALL=mean(race_data$driver_home)*100, 
    WIN=mean(race_data_win$driver_home)*100) ,
  main='Driver at Home by %'
  )
```





# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

ggplot()
  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
