---
title: "TidyTemplate"
date: 2021-08-17
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(zoo)
library(gt)
library(scales)
library(ggtext)
library(glue)
library(ggpubr)

theme_set(theme_minimal())

plot_theme <- theme(
    panel.grid.major = element_blank(),
    #panel.grid.minor = element_blank(),
    legend.position = "none" ,
    panel.background = element_rect(fill = "lightblue",
                                colour = "lightblue",
                                size = 0.5, linetype = "solid"
                                ),
  )


```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2022-03-22")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

babynames <- tt$babynames

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.




```{r Wrangle}

babynames2 <- babynames %>% 
  select(-prop) %>% 
  filter(!name %in% c('Baby' , 'Unnamed' , 'Unknown') ) %>% 
  group_by(sex , name ) %>% 
  mutate(prev_year = lag(n) ,
         raw_diff = rollapply(n, 2, diff, fill = NA) ,
         pct_change = (n/lag(n) - 1) * 100 , 
         five_ya = rollapply(n, 5, mean, fill = NA) , 
         five_ya_diff = rollapply(five_ya, 2, diff, fill = NA) ,
         five_ya_diff_abs = abs(five_ya_diff)) %>% 
  ungroup()

```





```{r fig.width=8,fig.height=5}
# get a list of 25 names who experienced the biggest percentage jump YoY
babynames_biggest_movers <- babynames2 %>% 
  filter(prev_year > 99) %>% 
  select(year , sex , name , n , prev_year , pct_change) %>% 
  arrange(desc(pct_change)) %>% 
  head(25 ) %>% 
  mutate(max_change = pct_change , max_year = year , max_n = n)

# filter data to only include biggest jumpers
babynames_biggest_movers_all <- babynames2 %>% 
  inner_join(babynames_biggest_movers %>% select(name , sex , max_change , max_year , max_n), by=c('name' = 'name' , 'sex'='sex'))


# facet plot of all names in list
big_jumps_plot_free <-  babynames_biggest_movers_all %>% 
  mutate(name = fct_reorder(name , pct_change)) %>% 
  ggplot(aes(x=year , y=n )) +
  geom_line() +
  facet_wrap(~name , scales='free_y' ) +
  theme(legend.position = "none") +
  labs(x='' , y='' , title = 'Baby Names that Experienced Biggest Jump' , 
       subtitle = 'Calculated: YoY Percentage Change (Only include names with at least 100 babies the previous year.)' , 
       caption = 'Plot: @itsnatrivera    Data: babynames R Package') +
  geom_text(
    data=babynames_biggest_movers_all,
    aes(label=max_year, x=max_year, y=max_n ), 
    inherit.aes = FALSE,
    color = 'blue',
    fontface = "bold",
    size=2.75 ,
    hjust=1
    ) +
  plot_theme


big_jumps_plot_free
```






```{r fig.width=8,fig.height=5}

# get a list of 25 names who experienced the biggest percentage drop YoY
babynames_biggest_movers_drops <- babynames2 %>% 
  filter(prev_year > 99) %>% 
  select(year , sex , name , n , prev_year , pct_change) %>% 
  arrange((pct_change)) %>% 
  head(25 ) %>% 
  mutate(max_change = pct_change , max_year = year , max_n = n)

# filter data to only include biggest droppers
babynames_biggest_movers_all_drops <- babynames2 %>% 
  inner_join(babynames_biggest_movers_drops %>% select(name , sex , max_change , max_year , max_n), by=c('name' = 'name' , 'sex'='sex'))



# facet plot of all names in list
big_drops_plot_free <-  babynames_biggest_movers_all_drops %>% 
  mutate(name = fct_reorder(name , pct_change)) %>% 
  ggplot(aes(x=year , y=n )) +
  geom_line() +
  facet_wrap(~name , scales='free_y' ) +
  theme(legend.position = "none") +
  labs(x='' , y='' , title = 'Baby Names that Experienced Biggest Drop' , 
       subtitle = 'Calculated: YoY Percentage Change (Only include names with at least 100 babies the previous year.)' , 
       caption = 'Plot: @itsnatrivera    Data: babynames R Package') +
  geom_text(
    data=babynames_biggest_movers_all_drops,
    aes(label=max_year, x=max_year, y=max_n ), 
    inherit.aes = FALSE,
    color = 'blue',
    fontface = "bold",
    size=2.75 ,
    hjust=1.25
    ) +
  plot_theme

big_drops_plot_free
```




```{r}
ggarrange(big_jumps_plot_free , big_drops_plot_free , ncol = 1)
```


```{r}

bar_chart <- function(value, color = "red"){
    
    glue::glue("<span style=\"display: inline-block; direction: ltr; border-radius: 4px; padding-right: 2px; background-color: {color}; color: {color}; width: {value}%\"> &nbsp; </span>") %>% 
    as.character() %>% 
    gt::html()
}


babynames_biggest_movers %>% 
  mutate(pct_change_plot = pct_change/max(pct_change) * 100,
         pct_change_plot = map(pct_change_plot, ~bar_chart(value = .x, color = "lightblue"))) %>% 
  select(name ,sex  , year , n , prev_year , pct_change, pct_change_plot) %>% 
  gt() %>% 
  cols_align(
    align = "left",
    columns = vars(pct_change_plot)
  )
```


```{r}
babynames2 %>% 
  group_by(year , sex) %>% 
  summarise(n=sum(n)) %>% 
  ggplot(aes(x=year , y=n , color=sex)) +
  geom_line()
```



# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


babynames %>% group_by(year , sex) %>% summarise(total_prop = sum(prop))

  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
