---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
library(camcorder)
library(ggtext)


theme_set(theme_minimal())
```


```{r}
gg_record(
  dir = 'temp/', # where to save the recording
  device = "jpeg", # device to use to save images
  width = 6,      # width of saved image
  height = 6,     # height of saved image
  units = "in",   # units for width and height
  dpi = 300       # dpi to use when saving image
)
```




```{r}
gg_resize_film(
  height = 6,
  width = 8,
  units = "in",
  dpi = 300
)
```



```{r}
gg_playback(
  name = 'child-care.gif',
  first_image_duration = 5,
  last_image_duration = 30,
  frame_duration = .5,
  image_resize = 800
)
```





```{r}
global_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/global_temps.csv')
nh_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/nh_temps.csv')
sh_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/sh_temps.csv')
zonann_temps <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-07-11/zonann_temps.csv')


```


lats <- unique(z_temps$name) |> 
  as.data.frame() |> 
  rename(range = 1) |>
  mutate(name = range) |>
  separate_wider_delim(range , delim = '-' , names=c('lower','upper')) |>
  mutate(lower_lat = ifelse( substr(lower ,3,3) == 'U' ,0, as.integer( substr(lower ,1,2))), 
         lower_lat = ifelse( substr(lower ,3,3) == 'S' , lower_lat*-1, lower_lat  ) ,
         upper_lat = ifelse( substr(upper ,3,3) == 'U' ,0, as.integer( substr(upper ,1,2))) , 
         upper_lat = ifelse( substr(upper ,3,3) == 'S' , upper_lat*-1, upper_lat  ) ) |>
  select(name , lower_lat , upper_lat)

z_temps <- z_temps |>
  left_join(lats) |>
  filter(! name %in% c('24N-90N' , '24S-24N' , '90S-24S')) 


```{r}
z_temps <- zonann_temps |>
  pivot_longer(cols = 5:15) |>
  mutate(decade = Year - Year %% 10) |>
  filter(! name %in% c('24N-90N' , '24S-24N' , '90S-24S')) 

z_decade <- z_temps |>
  group_by(decade , name ) |>
  summarise(temp = mean(value))

lat_ord <- c('90S-64S' , '64S-44S' , '44S-24S' , '90S-24S' , 
            "24S-EQU" , "EQU-24N" , "24S-24N" , "24N-44N" , 
            "44N-64N" , "64N-90N" , "24N-90N")



z_decade$name <- factor(z_decade$name, ordered = TRUE, levels = lat_ord )
```







```{r}
plt_title <- 'Latitude Zonal Mean Surface Temperature by Decade'
plt_subtitle <- '<br>The GISS Surface Temperature Analysis version 4 (GISTEMP v4) is an estimate of global surface temperature change.<br>'
plt_caption <- '**Data:** NASA GISS Surface Temperature Analysis (GISTEMP v4) via #TidyTuesday **Plot:** Nat Rivera @Itsnatrivera'

z_decade |>
  ggplot(aes(x=as.factor(decade) , y=name , fill=temp , label=round(temp , 1))) +
  geom_tile(color = "black", lwd = 0.25, linetype = 1) +
  geom_text(size = 3) +
  scale_fill_gradient2(low = "#18206F", mid = "#F5E2C8",high = "#BD1816" , limits = c(-1.5, 2.5)) +
  labs(x='' , y='' , title=plt_title , caption = plt_caption , subtitle = plt_subtitle) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    plot.title = element_textbox_simple(face = 'bold' , hjust = 0.5 , size = 18) ,
    plot.subtitle = element_textbox_simple() ,
    plot.caption = element_markdown() 
  )
```




```{r}

```









