---
title: "TidyTuesday_21-12-07"
date: 2021-12-07
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

theme_set(theme_minimal())

```

# Load the weekly Data

Dowload the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-12-07")

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

spiders <- tt$spiders

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

spiders %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}
# add a boolean for island
spiders <- spiders %>% 
  mutate(island = grepl('Is.' , distribution))

spiders$distinct_name <- paste( spiders$family , spiders$genus ,  spiders$species , spiders$subspecies)
```


```{r}
distribution <- spiders %>% 
  select(speciesId , distribution) %>% 
  mutate(dis_list = str_split(spiders$distribution , ',')) %>% 
  mutate(dist_to = grepl(' to ' , distribution)) %>% 
  mutate(dist_parentheses = grepl('\\(.{1,} to .{1,}\\)',distribution))
```



```{r}
# break down the distribution column
dist <- spiders %>% 
  select(speciesId , distribution) %>% 
  mutate(dis_list = str_split(spiders$distribution , ',')) %>% 
  unnest(dis_list) %>% 
  mutate(dis_list = str_trim(dis_list)) %>% 
  mutate(dis_to = grepl(' to ' , dis_list)) %>% 
  mutate(dis_list2 = str_replace(dis_list , '. Introduced to' , ' to')) %>% 
  mutate(dis_list3 = str_replace(dis_list2 , ' \\(.{1,}\\)' , '')) %>% 
  mutate(dis_list4 = str_replace(dis_list3 , '\\(.{1,}|.{0,}[a-z]{1,}\\)' , '')) %>% 
  mutate(two_to = grepl('.{1,} to .{1,} and .{1,} to .{1,}' , dis_list4))
```



```{r}
# split the dist df to those with two movements
dist1 <- dist %>% 
  filter(!two_to) %>% 
  select(speciesId , dis_list4) %>% 
  filter(dis_list4 != '')

# split the dist df to those with two movements
# split those rows with two movements to two rows
dist2 <- dist %>% 
  filter(two_to) %>% 
  select(speciesId , dis_list4) %>% 
  filter(dis_list4 != '') %>% 
  mutate(dis_list4 = str_split(dis_list4 , 'and')) %>% 
  unnest(dis_list4) %>% 
  mutate(dis_list4 = str_trim(dis_list4))


# union the data back
dist3 <- union_all(dist1,dist2) %>% 
  mutate(dis_to = grepl(' to ' , dis_list4))
```




```{r}
# list of countries where spiders are
countries <- dist3 %>% filter(!dis_to) %>% select(-dis_to)

# list of imports
imports <- dist3 %>% filter(dis_to) %>% select(-dis_to)

imports1 <- imports %>% 
  separate(dis_list4 ,sep =  ' to ',into = c('origin' , 'dest')) %>% 
  left_join(spiders ,by = 'speciesId') %>% 
  select(speciesId , origin , dest , year)

# split up the countries in the import list
countries <- imports %>% 
  mutate(dis_list4 = str_split(dis_list4 , ' to ')) %>% 
  unnest(dis_list4) %>% 
  union_all(countries) %>% 
  unique()
```



```{r}
dist %>% 
  filter(grepl('.{1,} to .{1,} and .{1,} to .{1,}' , dis_list)) %>% 
  select(dis_list)
```

```{r}
spiders %>% 
  filter(grepl('.{1,} to .{1,} and .{1,} to .{1,}' , distribution)) %>% 
  select(distribution)
```



```{r}
table(distribution$dist_to)
```


```{r}
unlist(str_split(spiders$distribution , ','))
```



# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}
spiders %>% 
  group_by(distribution) %>% 
  summarise(n=n()) %>% 
  ggplot(aes(y=distribution,x=n)) +
  geom_bar(stat = 'identity')
  
```

```{r}
dist <- spiders$distribution %>% 
  str_split(',') %>% 
  unlist() %>% 
  str_trim() %>% 
  as.data.frame() %>% 
  rename(distribution='.') %>% 
  group_by(distribution ) %>% 
  summarise(n=n() , .groups = 'drop') %>% 
  arrange(-n)

#ggplot(dist , aes())

head(dist,20)
```


```{r}
dist %>% 
  filter(grepl(' to ' , distribution)) %>% 
  filter(!grepl('\\(.{1,} to .{1,}\\)',distribution))
```


```{r}
sapply(spiders, n_distinct)
```

```{r}
spiders %>% 
  count(distinct_name) %>% 
  arrange(-n)
```


```{r}
spiders %>% 
  filter(species %in% c('fragilis' , ''))
```



```{r }
spiders %>% 
  count(family) %>% 
  mutate(family = fct_lump(family, 8, w = n, other_level = "All others")) %>% 
  group_by(family) %>% 
  summarise(n=sum(n) , .groups='drop') %>% 
  mutate(family = fct_reorder(family, n)) %>% 
  arrange(family)
```


```{r}
spiders %>% 
  count(family) %>% 
  mutate(family = fct_lump(family, 19, w = n, other_level = "All others")) %>% 
  group_by(family) %>% 
  summarise(n=sum(n) , .groups='drop') %>% 
  mutate(family = fct_reorder(family, n)) %>%
  ggplot(aes(x=n,y=family)) +
  geom_bar(stat='identity')
```


```{r}
spiders %>% 
  count(author) %>% 
  mutate(author = fct_lump(author, 19, w = n, other_level = "All others")) %>% 
  group_by(author) %>% 
  summarise(n=sum(n) , .groups='drop') %>% 
  mutate(author = fct_reorder(author, n)) %>%
  ggplot(aes(x=n,y=author)) +
  geom_bar(stat='identity')
```



```{r}
spiders %>% filter(substr(species,1,3)== substr(author,1,3))
```



```{r}
spiders %>% 
  count(year) %>% 
  ggplot(aes(x=year,y=n)) +
  geom_point() +
  geom_smooth(method=loess)
```


# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
