---
title: "TidyTemplate"
date: 2022-08-16
output: html_output
---

# TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggimage)
library(ggtext)
library(scales)
library(ggpubr)

theme_set(theme_minimal())

blue <- '#0474BA'  
orange <- '#F17720'
gray <- '#a9a9a9'


plot_theme <- theme(
    plot.title = element_markdown( hjust = 0.5 , padding = margin(0, 0, 0, 0)) ,
    plot.subtitle = element_markdown( size=10) ,
    plot.caption = element_markdown() ,
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    strip.background =element_rect(fill="gray" , linetype = 'blank'),
    strip.text = element_text(colour = 'white' , face='bold')
  )
```

# Load the weekly Data


# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

characters <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-08-16/characters.csv')
myers_briggs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-08-16/myers_briggs.csv')
psych_stats <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-08-16/psych_stats.csv')

```





```{r}
mb <- myers_briggs %>% group_by(myers_briggs) %>% summarise(total = sum(number_users))
mb
```




```{r}
dond <- psych_stats %>% filter(char_id == 'MM1')

dond

```



```{r}
# Split question column into two options
psych_stats[c('opt1', 'opt2')] <- str_split_fixed(psych_stats$question, '/', 2)

psych_stats$score <- as.integer( if_else(psych_stats$personality == psych_stats$opt2 , 
                                        psych_stats$avg_rating ,100-psych_stats$avg_rating))
```




```{r}

psych_wider <- psych_stats %>%
  select(char_name ,  uni_name , question , score ) %>% 
  pivot_wider(names_from = question, values_from = score , values_fn = sum) 
```



```{r}
psych_wider %>% ggplot( aes(x=`messy/neat`, y=`diligent/lazy`)) + geom_point()
```



```{r}
psych_wider %>% ggplot( aes(x=`morning lark/night owl`, y=`diligent/lazy`)) + geom_point()
```




```{r}
psych_wider %>% ggplot( aes(x=`feminist/sexist` , y=`diligent/lazy`)) + geom_point()
```


```{r}
psych_wider %>% ggplot( aes(x=`disorganized/self-disciplined` , y=`diligent/lazy`)) + geom_point()
```


```{r}
psych_lm <- psych_wider %>% select(`messy/neat`:`obedient/rebellious`)


lazy_lm <- lm(data = psych_lm , formula =`diligent/lazy`~.)
summary(lazy_lm)
```



```{r fig.width=8}
showa <- 'The Office'
showb <- 'Parks and Recreation'

psych_topr<- psych_wider %>% 
  filter(uni_name == showa |  uni_name == showb ) %>% 
  left_join(characters , by = c('char_name' = 'name')) 


psych_topr %>% 
  ggplot( aes(x=`chaotic/orderly` , y=	`angelic/demonic` , label = char_name )) + 
  geom_image(aes(image=image_link), size=0.05 ) +
  geom_text(nudge_y = -3 , size = 2.5 , check_overlap = TRUE) +
  facet_grid(~uni_name.x ) +
  #labs(title= paste(showa , '-' , showb)) +
  scale_x_continuous(breaks=c(0,50,100)) + 
  scale_y_continuous(breaks=c(0,50,100)) +
  scale_color_manual(values=c(blue, orange)) +
  theme(panel.border=element_blank(), axis.line=element_line())

```


```{r}
universe <- 'The Office'

psych_topr<- psych_wider %>% 
  filter(uni_name == universe  ) %>% 
  left_join(characters , by = c('char_name' = 'name')) 


psych_topr %>% 
  ggplot( aes(x=`chaotic/orderly` , y=	`angelic/demonic` , label = char_name )) + 
  geom_hline(yintercept=50) + 
  geom_vline(xintercept=50) + 
  geom_text(nudge_y = -6 , size = 2.5) + 
  #geom_text_repel(nudge_y = -4) + labs(title = "geom_text_repel()") +
  geom_image(aes(image=image_link), size=0.06 , asp=1.6) +
  geom_label(aes(x = 50, y = 5, label = "Angelic"), fill = "white") +
  geom_label(aes(x = 50, y = 95, label = "Demonic"), fill = "white") +
  geom_label(aes(x = 5, y = 50, label = "Chaotic"), fill = "white") +
  geom_label(aes(x = 95, y = 50, label = "Orderly"), fill = "white") +
  labs(title = paste('Psychometrics for charactors from<strong>' , universe , '</strong>' ), 
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  theme(
    plot.title = element_markdown(size = 16 , hjust=0.5) ,
    plot.caption = element_markdown() ,
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank())

```

```{r }
universe <- 'Parks and Recreation'

psych_topr<- psych_wider %>% 
  filter(uni_name == universe  ) %>% 
  left_join(characters , by = c('char_name' = 'name')) 


psych_topr %>% 
  ggplot( aes(x=`chaotic/orderly` , y=	`angelic/demonic` , label = char_name )) + 
  geom_hline(yintercept=50) + 
  geom_vline(xintercept=50) + 
  geom_text(nudge_y = -6 , size = 2.5) + 
  geom_image(aes(image=image_link), size=0.06 , asp=1.6 ) +
  geom_label(aes(x = 50, y = 5, label = "Angelic"), fill = "white") +
  geom_label(aes(x = 50, y = 95, label = "Demonic"), fill = "white") +
  geom_label(aes(x = 5, y = 50, label = "Chaotic"), fill = "white") +
  geom_label(aes(x = 95, y = 50, label = "Orderly"), fill = "white") +
  labs(title = paste('Psychometrics for charactors from<strong>' , universe , '</strong>' ), 
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  theme(
    plot.title = element_markdown(size = 16 , hjust = 0.5) ,
    plot.caption = element_markdown() ,
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank())

```



```{r }
universe <- 'Marvel Cinematic Universe'

psych_topr<- psych_wider %>% 
  filter(uni_name == universe  ) %>% 
  left_join(characters , by = c('char_name' = 'name')) 


psych_topr %>% 
  ggplot( aes(x=`chaotic/orderly` , y=	`angelic/demonic` , label = char_name )) + 
  geom_hline(yintercept=50) + 
  geom_vline(xintercept=50) + 
  geom_text(nudge_y = -6 , size = 2.5) + 
  geom_image(aes(image=image_link), size=0.06 , asp=1.6) +
  geom_label(aes(x = 50, y = 5, label = "Angelic"), fill = "white") +
  geom_label(aes(x = 50, y = 95, label = "Demonic"), fill = "white") +
  geom_label(aes(x = 5, y = 50, label = "Chaotic"), fill = "white") +
  geom_label(aes(x = 95, y = 50, label = "Orderly"), fill = "white") +
  labs(title = paste('Psychometrics for charactors from<strong>' , universe , '</strong>' ), 
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  theme(
    plot.title = element_markdown(size = 16 , hjust = 0.5) ,
    plot.caption = element_markdown() ,
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank())

```



```{r }
universe <- 'The Boys'

psych_topr<- psych_wider %>% 
  filter(uni_name == universe  ) %>% 
  left_join(characters , by = c('char_name' = 'name')) 


psych_topr %>% 
  ggplot( aes(x=`chaotic/orderly` , y=	`angelic/demonic` , label = char_name )) + 
  geom_hline(yintercept=50) + 
  geom_vline(xintercept=50) + 
  geom_text(nudge_y = -6 , size = 2.5) + 
  geom_image(aes(image=image_link), size=0.06 , asp=1.6 ) +
  geom_label(aes(x = 50, y = 5, label = "Angelic"), fill = "white") +
  geom_label(aes(x = 50, y = 95, label = "Demonic"), fill = "white") +
  geom_label(aes(x = 5, y = 50, label = "Chaotic"), fill = "white") +
  geom_label(aes(x = 95, y = 50, label = "Orderly"), fill = "white") +
  labs(title = paste('Psychometrics for charactors from<strong>' , universe , '</strong>' ), 
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  theme(
    plot.title = element_markdown(size = 16 , hjust = 0.5) ,
    plot.caption = element_markdown() ,
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank())

```

```{r fig.width=8}
showa <- 'The Simpsons'
showb <- 'Futurama'

psych_topr<- psych_wider %>% 
  filter(uni_name == showa |  uni_name == showb ) %>% 
  left_join(characters , by = c('char_name' = 'name')) 


psych_topr %>% 
  ggplot( aes(x=`chaotic/orderly` , y=	`angelic/demonic` , label = char_name )) + 
  geom_image(aes(image=image_link), size=0.07 ) +
  #geom_text(nudge_y = -3 , size = 2.5 ,  show.legend = FALSE) +
  facet_grid(~uni_name.x ) +
  scale_x_continuous(breaks=c(0,50,100)) + 
  scale_y_continuous(breaks=c(0,50,100)) +
  theme(panel.border=element_blank(), axis.line=element_line())

```








```{r}
psych_agg <- psych_wider %>% 
  left_join(characters , by = c('char_name' = 'name')) %>% 
  group_by(uni_name.x) %>% 
  summarise(`chaotic   orderly` = mean(`chaotic/orderly`) , 
            `angelic   demonic` = mean(`angelic/demonic`) , 
            notes = mean(notability)) %>% 
  arrange(notes, .by_group = TRUE) %>%
  top_n(80)

psych_agg %>% 
  ggplot(aes(x=`chaotic   orderly` , y = `angelic   demonic` , label=uni_name.x)) +
  #geom_point(show.legend = FALSE) +
  geom_text(size=2.5 )
```



```{r}
mb_quants <- myers_briggs %>% 
  mutate(intro = ifelse(substr(myers_briggs,1,1) == 'I' , 'Introvert','Extrovert')) %>% 
  group_by(myers_briggs , intro ) %>% 
  summarise(max_users = max(number_users) , min_users = min(number_users) , .groups='drop') %>% 
  mutate(myers_briggs = fct_reorder(myers_briggs, max_users, .desc = FALSE))
  

mb_quants %>% 
  ggplot(aes(x=max_users , y=myers_briggs , fill=intro , label=comma(max_users))) +
  geom_bar(stat='identity' , show.legend = FALSE) +
  geom_text(nudge_x = 800 , size=3) +
  scale_fill_manual(values=c(gray, blue)) +
  labs(title = 'Far more <strong style="color:#0474BA">Introverts</strong> filled out the survey than <strong style="color:#a9a9a9">Extroverts</strong>' , 
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  theme(
    plot.title = element_markdown(size = 16) ,
    plot.caption = element_markdown() ,
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())
```

```{r }
 # Basic piechart
mb_quants %>% 
  group_by(intro ) %>% 
  summarise(cnt = sum(max_users)) %>%
  mutate(freq = round(cnt / sum(cnt), 3)) %>% 
  ggplot(aes(x='', y=freq, fill=intro , label = freq )) +
  geom_bar(stat="identity", width=2 , show.legend = FALSE) +
  annotate(geom="text", x = '', y = 0.30, label = '71%') +
  annotate(geom="text", x = '', y = 0.80, label = '29%') +
  coord_polar("y", start=0) +
  scale_fill_manual(values=c(gray, blue)) +
  labs(title = '<strong style="color:#a9a9a9">Extroverts</strong> vs <strong style="color:#0474BA">Introverts</strong>' , 
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  theme(
    plot.title = element_markdown(size = 16 , hjust = 0.5) ,
    plot.caption = element_markdown() ,
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank())
```


```{r}
myers_briggs %>% 
   group_by(myers_briggs) %>%
   filter(avg_match_perc == max(avg_match_perc)) %>%
   select(myers_briggs , uni_name  , char_name , avg_match_perc , number_users)
```


theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank() ,
        axis.text.y=element_blank())


```{r }
myers_psych_agg_tops <- myers_briggs %>% 
  select(uni_name , char_name , myers_briggs , avg_match_perc) %>% 
  group_by(char_name ) %>% 
  slice_max(n=1 , order_by=avg_match_perc) %>% 
  left_join(psych_stats , by = 'char_name') %>% 
  filter(nchar(personality) > 1) %>%  # filter out emoji
  group_by(myers_briggs , question , personality) %>% 
  summarise(avg_match = mean(avg_rating) , .groups='drop') %>% 
  group_by(myers_briggs) %>% 
  slice_max(n=5 , order_by=avg_match) %>% 
  mutate(phys_ranks = order(order(avg_match, myers_briggs, decreasing=FALSE)))

mb_pers <- myers_psych_agg_tops %>%   
  ggplot(aes(x=avg_match , y= reorder(personality ,phys_ranks) )) +
  geom_bar(stat='identity' ,fill=blue) + 
  geom_text(aes(label = round(avg_match,0)) ,
                 nudge_x = 10 , size=2.25 , fontface='bold') +
  geom_text(aes(x=2 ,label = personality ) , size=2.25 , hjust=0 ,color='white' , fontface='bold')+
  facet_wrap(~myers_briggs , nrow = 4 , scales='free_y' ) +
  scale_fill_manual(values=c(blue)) +
  labs(title = '<strong>Top Personality Traits per Myers Briggs Type</strong>' , 
       subtitle = 'Extraversion vs. Introversion | Sensing vs. Intuition | Thinking vs. Feeling | Judging vs. Perceiving' ,
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  plot_theme
  

mb_pers
```



```{r}
(substr(myers_psych_agg_tops$personality,1,1)  ) == '\\'
```



```{r }
char_myers_top <- myers_briggs %>% 
  left_join(characters %>% select(name,image_link) , by = c('char_name'='name')) %>% 
  select(myers_briggs , uni_name , char_name , avg_match_perc , image_link) %>% 
  group_by(char_name ) %>% 
  slice_max(n=1 , order_by=avg_match_perc) %>% 
  group_by(myers_briggs ) %>% 
  slice_max(n=5 , order_by=avg_match_perc , with_ties=FALSE) %>% 
  mutate(char_ranks = order(order(avg_match_perc, myers_briggs, decreasing=FALSE)))

mb_bars <- char_myers_top %>%   
  ggplot(aes(x=avg_match_perc , y= reorder(char_name,char_ranks) )) +
  geom_bar(stat='identity' , fill=blue ) + 
  geom_image(aes(x= -10 , image=image_link), size=0.1 , asp=1.6 ) +
  geom_text(aes(x=2 ,label = paste0(char_name,' (',uni_name , ')')) , 
            size=2.0 , hjust=0 ,color='white' , fontface='bold')+
  geom_text(aes(label = round(avg_match_perc,0)) , 
            nudge_x = 10 , size=2.0 , fontface='bold') +
  facet_wrap(~myers_briggs , nrow = 4 , scales='free_y'  ) +
  labs(title = '<strong>Characters that Matched Highest with each Myers Briggs Type</strong>' , 
       subtitle = 'Extraversion vs. Introversion | Sensing vs. Intuition | Thinking vs. Feeling | Judging vs. Perceiving' ,
       caption = '<strong>Data:</strong> opensychometrics.org <strong>Plot:</strong> @itsnatrivera') +
  plot_theme

mb_bars
```



```{r}
fold <- '/Users/natrivera/TidyTuesdayR/2022/2022-08-16/'
write_csv(char_myers_top , paste0(fold,'char_myers_top.csv'))
write_csv(myers_psych_agg_tops , paste0(fold,'myers_psych_agg_tops.csv') )
```



```{r fig.height=3 , fig.width=1.5}
ggarrange(mb_bars , mb_pers , 
          ncol = 1, nrow = 2)
```


```{r}
isfp <- myers_briggs %>% filter(myers_briggs=='ISFP')
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}



  
```


